### 2016-01-06 p2/abstract.tex
Fix typo

These results are often intuitive,
but providing exact proofs for them is far from trivial.
They contribute to our understanding of this special type of algebraic model,
and toward building more complete algebras
of filesystems 
and extedning algebraic approaches to other data storage protocols.
They also form a theoretical basis for
specifying
and guaranteeing the error-free operation
of applications that implement an algebraic approach to synchronization.

>>>>

These results are often intuitive,
but providing exact proofs for them is far from trivial.
They contribute to our understanding of this special type of algebraic model,
and toward building more complete algebras
of filesystems 
and extending algebraic approaches to other data storage protocols.
They also form a theoretical basis for
specifying
and guaranteeing the error-free operation
of applications that implement an algebraic approach to synchronization.
